Modern Graph Generators: A Survey

### 2018-11-27 challenges.tex
fixed some plagiarism issues from page 19 and on

The respective data generator should hence be able to simulate a natural growth
and/or changes in the structure of the graph with regards to the various
features of distinct use cases. However,  even though the area of dynamic graphs
is intensively studied, surprisingly there seem to exist only very few proposals
of a generator for dealing with this area.
In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering
dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
of nodes into natural groups based on the paradigm of intra-cluster density
versus inter-cluster sparsity of edges. The generator generates a time series
of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
successive atomic updates like for instance, the insertion of a vertex or the removal of an
edge. The generator monitors the (dynamic) ground truth clustering and the probability
of the atomic events is chosen in such a way that the ground truth clustering is
maintained while the randomness of the generated graph is kept.

@@

Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
and propose an ``edge local differential privacy'' based graph generation
method. The proposed method allows generating privacy preserving synthetic social
graphs without the need of a centralized data curator, while preserving structural
properties more accurately than straw-hat methods such as Randomized
Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
Degree-based Graph Generation (which perturbates the original graph degrees
using the Laplace mechanism~\cite{dwork2009differential}). Again, even though the
proposed technique outperforms the baselines, the results show that there is
still room for improvement in terms of the structural properties of the
generated graph.

>>>>

The respective data generator should hence be able to simulate a natural growth
and/or changes in the structure of the graph with regards to the various
features of distinct use cases. However,  even though the area of dynamic graphs
is intensively studied, surprisingly there seem to exist only very few proposals
of a generator for dealing with this area.
In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering
dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
of nodes into natural groups based on the concept of intra-cluster
versus inter-cluster density of edges. The generator generates a time series
of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
successive atomic updates like for instance, the insertion of a vertex or the removal of an
edge. The generator dynamically monitors the ground truth clustering, and the probability
of the updates is chosen in such a way that the ground truth is
maintained while the randomness of the generated graph is kept.

@@

Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
and propose an ``edge local differential privacy'' based graph generation
method. The proposed method allows generating privacy preserving synthetic social
graphs without the need of a centralized data curator, while preserving structural
properties more accurately than straw-hat methods such as Randomized
Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
Degree-based Graph Generation (which perturbates the original graph degrees
using the Laplace mechanism~\cite{dwork2009differential}). Again, even though the
proposed technique outperforms the baselines, the results show that there is
still room for improving the structural properties of the
generated graph.

### 2018-11-27 generators_community_detection.tex
fixed some plagiarism issues from page 19 and on

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of various sizes with a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which consists of the percentage of
edges in the graph connecting nodes that belong to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by considering the described constraints.

>>>>

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of diverse sizes and
densities. The generated communities follow a power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which consists of the percentage of
edges in the graph connecting nodes that belong to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process is implemented as an optimization process starting with an empty graph and 
progressively filling it with nodes and edges guided by the specified constraints.
